### 2016-06-09 paper/evaluation.tex
One more

\section{Evaluation}
We ran our algorithm on tests validating our ability to handle regular
expression equivalences, tests derived from the Augeus test suite, and from
tests derived from the FlashFill tests.

>>>>

\section{Evaluation}
We ran our algorithm on tests validating our ability to handle regular
expression equivalences, tests derived from the Augeus test suite, and from
tests derived from the FlashFill tests.\bcp{Need to carefully explain our
  experimental setup and methodology (on what machine config, how many test
  runs, what kind of statistics, ...)}
